Storing messages with multipartite neural cliques

### 2014-07-11 Articles/article.tex
...

@@

@@

	As information is shared across connections with multiple activated units per cluster, they are more resilient to network damages (for one message information is carried by $a^2 {c \choose 2}$ edges. $v_c$ will indicate a correct unit that should be activated, $v$ the other type of units.

>>>>

		Associative memories

		Recently, a new type of associative memories was proposed by Gripon and Berrou \cite{GriBer20117}.

		GBNN can also be used to retrieve messages from erroneous versions of them. We derive a formula for error rate in case of errors on messages.

		Fault tolerance of those networks was extensively studied in \cite{LedGriRabGro20145}. We extend this to multipartite cliques and show significant improvements in resilience to faults.

@@

	Our goal is to store messages so as to be able to retrieve them from partial or erroneous versions of them.

@@

	As information on a message is shared across connections with multiple activated units per cluster, they are more resilient to network damages (for one message information is carried by $a^2 {c \choose 2}$ edges. $v_c$ will indicate a correct unit that should be activated, $v$ the other type of units.
